%====================================================================================================
\begin{abstractpage}{Acknowledgments}
    \phantomsection
    \addcontentsline{toc}{chapter}{Acknowledgments}
    %====================================================================================================
    Nothing I have ever achieved would have been possible if not for my family who supported me
    when I went to study abroad and are always there waiting for me when I return.
    Ačiū mama, tėti, močiute, Jolita -- ačiū jums už viską, ką man suteikiate ir ką dėl manęs padarėte.
    Ačiū net Boltui ir Deilui, kurie galbūt ir nežino, ką aš veikiu, bet visuomet džiaugiasi mane matydami.

    I want to thank my friends who, despite the distance between us, are still people I can rely on, talk with,
    laugh with, and meet with whenever we like.
    Ačiū Martynai, Viliau ir Lukai, už neblėstančią draugystę nuo pat mokyklos ir universiteto laikų.
    Už visas tas valandas kurias praleidžiame kartu ir virtualiai.
    Be jūsų mano gyvenimas būtų be galo pilkesnis.

    I want to thank the amazing people whom I have had the pleasure to work with at DESY.
    Namely, my supervisor, Kerstin Tackmann, who has provided me with the chance to be a part of the science community
    and supported me in my research throughout the years.
    I want to thank the rest of the group: Arthur Bolz, Lu Cao, Markus R\"ohrken, Simon Wehle, and Ilya Komarov, who guided me to become a better researcher.
    My deepest thanks go to Sasha Glazov without whose support and advice the work of this thesis would likely not have materialised.
    I also want to express my gratitude to Carsten Niebuhr for his excellent leadership of the Belle~II group at DESY,
    and Andreas Gellrich who makes sure that the technical side of the work is always on top.
    I am also grateful to Frank Tackmann, Bahman Dehnadi and Ivan Novikov for their support in the theoretical side of the analysis.

   
    The nicest thing is that I not only worked with people at DESY, but I found friends.
    I want to thank all of you for helping me stay sane and:
    Maria Konstantinova, for being someone that I never expected to find here and yet nothing better could have ever happened to me;
    Sascha Dreyer, for our survival of the pandemic, shift parties and wine evenings;
    Navid K. Rad, for every meter that we climb up and fall off walls;
    Anselm Baur, for being a great office neighbour and our trips to Obi;
    Munira Khan, for all our self-deprecating humour that makes the day;
    Filippo Dattola, Alberto Martini, per ogni volta che ho parlato con voi in italiano;
    Cyrille Praz, for introducing us to the Brew Dog evenings;
    Michel Hern\'andez Villanueva, for some of the best Mexican food ever;
    Varghese Babu, for the incredible Indian cuisine;
    Tommy Martinov, for providing some of the funniest banter;
    Merle Graf-Schreiber, for enduring some of the \textit{best} TV shows together;
    Marcel Hohmann, for coming over all the way from down under to become the bingo master;
    Abtin Narimani, for all the fun evenings and life advice;
    Michael de Nuccio, for the positivity and playfulness I always feel when hanging out;
    Eldar Ganiev, for your good energy and humour, and for being the first to present my analysis to the wider world;
    and everyone else who I inevitably forget but appreciate not a tiny bit less.

    To everyone who took the time to give me comments on this thesis.
    I do not need to list you, but I want you to know that without your help I would have never succeeded.

    %====================================================================================================

\end{abstractpage}
