    %====================================================================================================
    \begin{abstractpage}{Disclaimer}
        \phantomsection
        \addcontentsline{toc}{chapter}{Disclaimer}
        %====================================================================================================
    
        The analysis of \BtoXsgamma presented in this thesis has been proposed to me by Prof.~Dr.~Kerstin Tackmann, 
        who supervised my work.
        Throughout the years I have also received constant feedback from Dr.~Arthur Bolz, Dr.~Lu Cao, Dr.~Markus R\"ohrken, Dr.~Ilya Komarov,
        Dr.~Simon Wehle, and many other Belle~II colleagues.
        The data used in the analysis has been provided by the Belle~II collaboration.
        The electron and positron beams are provided by the SuperKEKB collider.
        The work presented in \Cref{ch:analysis} is designed and performed primarily by me, with the support of the aforementioned people.
        It has been documented in a preprint, available in Ref.~\cite{Belle-II:2022hys}.
        The photon detection efficiency data-to-simulation comparison was performed by me and Dr. Simon Wehle, continuing the work that was set up by Dr. Natalia Kovalchuk and Prof. Dr. Torben Ferber.
        This has been documented in the Belle~II public note in Ref.~\cite{Henrikas:2604}.
        Additional studies performed by other members of the Belle~II collaboration, necessary for \BtoXsgamma, but not part of the original work of this thesis,
        are clearly named so in the text. Namely:
        \begin{itemize}
            \item The \FEI algorithm, its calibration and inclusion to the \basftwo (\Cref{sec:tag_reconstruction,sec:fei_calibration});
            \item The \ZMVA training and inclusion to the \basftwo  (\Cref{sec:selection_clusZMVA});
            \item The \piz and $\eta$ veto, validation on data and their inclusion to the \basftwo (\Cref{sec:selection_vetos,sec:piz_eta_calibration}).
        \end{itemize}
        The global fit of \BtoXsgamma experimental results (\Cref{sec:input_to_theory}) was performed by the SIMBA collaboration.
        The work discussed in \Cref{sec:future_prospects} has been performed based on the studies of \Cref{ch:analysis} and included in a co-authored preprint in Ref.~\cite{Belle-II:2022cgf}.
        I have also co-authored publications with the Belle~II tracking group, documented in Ref.~\cite{BelleIITrackingGroup:2020hpx}.
        As a member of the Belle~II collaboration, I co-authored many other publications and conference notes, which are not presented in this thesis.
        \footnote{{\scriptsize\url{https://inspirehep.net/literature?q=Henrikas\%20Svidras\%20or\%20H.\%20Svidras}}}.
        
        All of the text in this thesis has been worded by me.
        The figures that have not been produced by me are clearly indicated as such with a credit or a reference to the source.

        %====================================================================================================
    \end{abstractpage}
        %====================================================================================================