\chapter{Introduction}\label{sec:introduction}

The Standard Model is a theory describing the fundamental particles and their interactions that constitute the Universe.
The predictive power and precision of the Standard Model is arguably unmatched by any other theory in science.
The Higgs boson was proposed already in 1964 \cite{PhysRevLett.13.508}, more than 50 years before its discovery \cite{ATLAS:2012yve,CMS:2012qbp}.
The top quark was discovered \cite{PhysRevLett.74.2632,PhysRevLett.74.2626} two decades after the existence of the third generation of fermions was inferred \cite{HARARI1975265}.

However, some experiments do show, as of yet, unexplained tensions with the Standard Model. 
A notable example is the measurement of the anomalous magnetic moment of the muon \cite{PhysRevLett.126.141801}.
Although the Standard Model is able to provide an astounding 8 significant digit agreement with experiment, there is a disagreement at higher precision.
Similarly, for the case of anomalous magnetic moment of the electron, there is a tension between different experimental approaches \cite{PhysRevLett.100.120801,Morel:2020dww,Li:2021koa}.
The Standard Model has also not been able to provide a clear candidate for the excess matter that is observed in the Universe (dark matter).
Furthermore, the observed matter-antimatter asymmetry 
is larger than what is currently predicted in the Standard Model.
The mathematical framework of the Standard Model, while incredibly powerful, appears to be arbitrary, with numerous free parameters in the Standard Model.
For example, the existence of exactly 3 generations of fermions with a mass hierarchy is not theoretically well-grounded, but seems too organised to be accidental.
The strong force conserves the charge-parity symmetry, although it is not required by the Standard Model framework (strong CP problem).
There are many other experimental and theoretical inconsistencies (see Ref.~\cite{Ellis:2002wba} for a review) that cannot be addressed by the Standard Model in a satisfactory way.

These theoretical and experimental challenges motivate the search for discoveries that could lead to new developments in one of the most successful theories of science.
While there are numerous extensions to the Standard Model that have been proposed by the particle physics theory community, there is no clear evidence that any of them is the correct description of our Universe.
At the moment, it seems that hints about a clear direction can only come from more precise measurements that will test the Standard Model particle properties, interactions and process rates.

This thesis contributes such a measurement in the radiative decay of the beauty quark, where it transitions to a strange quark and a photon.
The measurement will be performed by studying data of $B$ mesons decaying into a meson system originating from an $s$ quark, $X_s$, and an energetic photon \g.
The data that is analysed was collected in 2019-2020 by the Belle II detector, which is located in Tsukuba, Japan at the KEK laboratory.
Belle II collects data of electron-positron collisions, provided by the SuperKEKB collider.
The colliding electron and positron beams create \FourS resonances which decay into pairs of \B mesons.

The standard notation of the radiative $B$ meson decay processes is adopted to label it as \BtoXsgamma.
This decay channel is sensitive to particles not included within the Standard Model. 
Furthermore, the parameters of the photon energy spectrum are important inputs to other precision measurements of the Standard Model.
A technique called hadronic-tagging, which reconstructs the partnering $B$-meson, yielding a purer final measured data sample.


These aforementioned points will be discussed in detail in this thesis.
The thesis is therefore split up in X chapters:
\todo[inline]{chapter later}
\todo[inline]{review and finish this chapter later}

